\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
fixes in the graph processing section, again

%\textbf{Orders induced by a graph.}
A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $v_1 \preceq_g v_2$ iff there is a path from $v_1$ to $v_2$ and there is no path from $v_2$ to $v_1$.
%Let $\opn{TOs}\left( g \right)$ be the set of total orders $o$ such that $\preceq_g \subseteq o$.
For example, $\preceq_h = \aset{\left( c_1,c_3 \right)}$. % and $\opn{TOs}\left( h \right)$ is the set of all permutations of $\aseq{c_1,c_2,c_3,c_4}$ in which $c_1$ comes before $c_3$.
%\textbf{Equivalence relation induced by a graph.}
A directed graph $g$ \emph{induces an equivalence relation} $\sim_g$ on its vertices defined such that $v_1 \sim_g v_2$ iff $v_1$ and $v_2$ belong to the same strongly connected component. We write $\left[ v \right]_g$ for the equivalence class of $v$ under $\sim_g$.
%\textbf{Linearizations of a dependency graph.}
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every pair of vertices $v_1,v_2\in V\left( g \right)$, $v_1 \preceq_g v_2$ implies $v_1 \ll v_2$, and if $v_1 \sim_g v_2$ and $ v_1 <_{\left[ v_1 \right]} v_2$ hold then $v_1 \ll v_2$.
%\textbf{Partial order on graphs.}

@@

\textbf{Lemma 1}
Assume that: $g_1$ and $g_2$ are two dependency graphs; 
for every pair of non-commutative commands $c_1,c_2 \in V\left(g_2\right)$, either $\left( c_1,c_2 \right)\in E\left( g_2 \right)$ or $\left( c_2,c_1 \right)\in E\left( g_2 \right)$;
$g_1 \leq g_2$;
$l_1$ is a linearization of $g_1$ and $l_2$ is a linearization of $g_2$. 
Then we have (a), $\bot\bullet l_1 \preceq \bot\bullet l_2$, and (b), if $g_1 = g_2$ then $\bot\bullet l_1 = \bot\bullet l_2$.

>>>>

%\textbf{Orders induced by a graph.}
A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $v_1 \preceq_g v_2$ iff there is a path from $v_1$ to $v_2$ and there is no path from $v_2$ to $v_1$.
%Let $\opn{TOs}\left( g \right)$ be the set of total orders $o$ such that $\preceq_g \subseteq o$.
For example, $\preceq_h = \aset{\left( c_1,c_3 \right)}$. % and $\opn{TOs}\left( h \right)$ is the set of all permutations of $\aseq{c_1,c_2,c_3,c_4}$ in which $c_1$ comes before $c_3$.
%\textbf{Equivalence relation induced by a graph.}
A directed graph $g$ \emph{induces an equivalence relation} $\sim_g$ on its vertices defined such that $v_1 \sim_g v_2$ iff $v_1$ and $v_2$ belong to the same strongly connected component. We write $\left[ v \right]_g$ for the equivalence class of $v$ under $\sim_g$.
%\textbf{Linearizations of a dependency graph.}
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every pair of vertices $v_1,v_2\in V\left( g \right)$, $v_1 \preceq_g v_2$ implies $v_1 \ll v_2$, and if $v_1 \sim_g v_2$ and $ v_1 <_{\left[ v_1 \right]_g} v_2$ hold then $v_1 \ll v_2$.
%\textbf{Partial order on graphs.}

@@

\textbf{Lemma 1}
Assume that: $g_1$ and $g_2$ are two dependency graphs; 
for every pair of non-commutative commands $c_1,c_2 \in V\left(g_2\right)$, either $\left( c_1,c_2 \right)\in E\left( g_2 \right)$ or $\left( c_2,c_1 \right)\in E\left( g_2 \right)$;
$g_1 \leq g_2$;
$l_1$ is a linearization of $g_1$ and $l_2$ is a linearization of $g_2$. 
Then we have (a), $\bot\bullet l_1 \sqsubseteq \bot\bullet l_2$, and (b), if $g_1 = g_2$ then $\bot\bullet l_1 = \bot\bullet l_2$.
